---
title: "p8105_hw6_nl2835"
author: "Nancy Le"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(collapse = TRUE, message = FALSE)
library(rnoaa)
library(modelr)
library(mgcv)

set.seed(1)
```

## Problem 2

```{r Central Park weather data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())

```

```{r bootstrapping}
boot_sample = function(weather_df) {
  sample_n(weather_df, size = nrow(weather_df), replace = TRUE)
}
```



```{r bootstrap regression}
bootstrap_reg <- function(df) {
  regression <- lm(tmax ~tmin + prcp, data = df)
  r2 <- summary(regression)$r.squared
  beta_1 <- coef(regression)["tmin"]
  beta_2 <- coef(regression)["prcp"]
  beta_inter <- beta_1 * beta_2 
  
  if (beta_inter <= 0) {
    logbetainter <- NA } else {
      logbetainter <- log(beta_inter)
    }
  
  tibble(r2 = r2, logbetainter = log(beta_inter))
}

boot_straps <- 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, ~boot_sample(weather_df)), 
    bootstrap_results = map_dfr(strap_sample, ~bootstrap_reg(.x |> as_tibble()))
  )
```

```{r}
boot_straps
```


```{r plot estimates of R2}
ggplot(boot_straps, aes(x = bootstrap_results$r2)) +
  geom_histogram(binwidth = 0.01, fill = "blue", color = "black") + 
  labs(title = "R-squared Estimates Distribution", 
       x = "R^2",
       y = "Frequency")
```

The distribution of r-squared estimates centers around R2 = 0.92 and is a symmetric distribution. 

```{r plot estimates of log(beta interecepts)}
ggplot(boot_straps, aes(x = bootstrap_results$logbetainter)) +
  geom_histogram(binwidth = 0.05, fill = "lightgreen", color = "black") + 
  labs(title = "Log Interaction Estimates", 
       x = "log(beta1*beta2)",
       y = "Frequency")
```

The distribution of log(b0 * b1) estimates is skewed left, with a median around -6. 

```{r compute r2 CI}
r_squared_quantiles <- quantile(boot_straps$bootstrap_results$r2, probs = c(0.025, 0.975), na.rm = TRUE)
```

```{r compute log CI}
logbetainter_quantiles <- quantile(boot_straps$bootstrap_results$logbetainter, probs = c(0.025, 0.975), na.rm = TRUE)
```

```{r print values}
r_squared_quantiles
logbetainter_quantiles
```


## Problem 3
```{r load birthweight csv file}
birthweight <-
  read.csv("./local/birthweight.csv") |> 
  janitor::clean_names() |> 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace), 
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) |> 
  na.omit()
```


```{r model}
fit = lm(bwt ~ ppwt, data = birthweight)

fit |> 
  broom::tidy() 
```

My proposed regression model is based on the hypothesis that baby's birthweight depends on the mother's pre-pregnancy weight (in pounds). 

```{r add residuals and predictions}
birthweight |> 
  modelr::add_residuals(fit) |> 
  modelr::add_predictions(fit) |> 
  ggplot(aes(x = ppwt, y = bwt)) + geom_point()
```

Within my model, I'm adding the residuals and fitted values to the birthweight dataframe.

```{r blength and gaweeks model}
fit_2 = lm(bwt ~ blength + gaweeks, data = birthweight)

fit_2 |> 
  broom::tidy() 

```

```{r bhead, blength, babysex, and interactions}
fit_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)

fit_3 |> 
  broom::tidy() 

```

```{r}
birthweight |> 
  gather_predictions(fit_2, fit_3) |> 
  ggplot(aes(x = bwt, y = blength)) + 
  geom_point() +
  geom_line(aes( y = pred), color = "red") + 
  facet_wrap(~model)
```


```{r rmse}
rmse(fit, birthweight)
rmse(fit_2, birthweight)
rmse(fit_3, birthweight)
```


```{r adding residuals and predictions}
birthweight <- birthweight |> 
    modelr::add_residuals(fit) |> 
    modelr::add_predictions(fit) |>
    modelr::add_residuals(fit_2) |> 
    modelr::add_predictions(fit_2) |>
    modelr::add_residuals(fit_3) |> 
    modelr::add_predictions(fit_3)  
    
```









